Array

### 2013-12-17 PAPERS/Report/AdvancedTypes/AdvancedTypes.tex
Fixing the rules to support array

TODO: This function updates the Name function ?
TODO: Integrate with EXPArray
% Rule to get a element in array, it can be used in become equal or Expressions
\begin{align*}
\lefteqn{\trad{n}{lvalue} \isdef} \\
& \LET t = \llvm{"\PH{\trad{\B{n.type}}{Type}} *"} \IN \\
& \quad \IF \mbox{\B{n} is a local variable} \THEN \llvm{""} \sep \local(\B{n}) \sep t \\
& \quad \IF \mbox{\B{n} is an array} \THEN \LET v = \variable \IN \trad{n}{AccessArray}  \sep v \sep t \\
& \quad \ELSE \LET v = \variable \IN \\
& \quad \quad \llvm{"\PH{v} = getelementptr \PH{\state(\B{n.root})}* \%self\$,} \\
& \quad \quad \quad \llvm{i32 0, i32 \PH{\idx(\B{n})} \nl"} \sep v \sep t
\end{align*}

%The new rule created 
%It can appear in LHS or RHS in become equal 
% We cannot use the tal function, because it is not able to solve any 
% expressions.
 - Não poderemos usar a função Tal, pois ela não resolverá expressões quaisquer!
\begin{align*}
\lefteqn{\trad{n}{AccessArray} \isdef} \\
&  \LET p_1 \sep v_1 \sep t_1  = \trad{base}{Exp}  \IN \\
&  \LET p_2 \sep v_2 \sep t_2  = \trad{indices}{Exp}  \IN \\
&  \LET v =  \variable  \IN \\
&  \llvm{"\PH{p_1} \PH{p_2} \PH{v} =  getelementptr \PH{t_1}, \PH{v_1}, i32 0, 
i32  \PH{v_2}\nl"} \sep v\\
&  \llvm{"\PH{v} = getelementptr \PH{\state(\B{n.root})}* \%self\$,\stateindex(\B{n.index,n.type})  \nl"}\\
\end{align*}

>>>>

TODO: This function updates the Name function ?
% Rule to get a element in array, it can be used in become equal or Expressions
\begin{align*}
\lefteqn{\trad{n}{lvalue} \isdef} \\
& \LET t = \llvm{"\PH{\trad{\B{n.type}}{Type}}"} \IN \\
& \quad \IF \mbox{\B{n} is a local variable} \THEN \llvm{""} \sep \local(\B{n}) \sep t \\
& \quad \IF \mbox{\B{n} is an array} \THEN \LET v = \variable \IN \trad{n}{ArrayItem}  \sep v \sep t \\
& \quad \ELSE \LET v = \variable \IN \\
& \quad \quad \llvm{"\PH{v} = getelementptr \PH{\state(\B{n.root})}* \%self\$,} \\
& \quad \quad \quad \llvm{i32 0, i32 \PH{\idx(\B{n})} \nl"} \sep v \sep t
\end{align*}

% We cannot use the tal function, because it is not able to solve any 
% expressions.

The rule ArrayItem is applied in expressions as ``$a(n1,...,n_{n})$'', where $a$ is n.base 
and $n1,...,n_{n}$ is a sequence of indices to select an item from array.

\begin{align*}
\lefteqn{\trad{n}{ArrayItem} \isdef} \\
&  \LET p_1 \sep v_1 \sep t_1  = \trad{n.base}{Exp}  \IN \\
&  \LET p_2 \sep v_2 \sep t_2  = \trad{n.indices}{\ListOf{Exp}}  \IN \\
&  \LET v =  \variable \AND  t = \trad{\B{n.type}}{Type}  \IN \\
&  \llvm{"\PH{p_1} \PH{p_2} \PH{v} =  getelementptr \PH{t_1}, \PH{v_1}, i32 0, i32  \PH{v_2}\nl"}  \sep v \sep t\\
\end{align*}
